---
title: "FINALCODE"
author: "MEZIANE YACINE"
date: "`r Sys.Date()`"
output: html_document
---

```{r} setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Checking the R version
```{r}
RStudio.Version()
```
## Les Packages
```{r}
library(tidyverse)
library(tidymodels)
library(tidyselect)
library(MLmetrics)
library(lightgbm)
library(data.table)
library(moments)
library(moments)
library(MLmetrics)
library(ggthemes)
library(ggmosaic)
library(gridExtra)
library(repr)
library(data.table)
library(fastDummies)
library(tictoc)
library(naniar)
library(DataExplorer)
library(lubridate)
library(patchwork)
library(corrplot)
library(kableExtra)
library(themis)
library(doParallel)
options(warn=-1)
options(scipen = 99)
```

##Upload Data
```{r}
train_iden <- read_csv("/Users/macmo/Desktop/Mémoire/Base de donnée/ieee-fraud-detection/train_identity.csv")
train_trans <- read_csv("/Users/macmo/Desktop/Mémoire/Base de donnée/ieee-fraud-detection/train_transaction.csv")
```
#creating full data
```{r}
data<- train_trans  %>% 
  left_join(train_iden,by="TransactionID")
rm(train_iden,train_trans)
```
#checking the target variable
```{r}
summary(data$isFraud)
```
#Summary data
```{r}
num_observations <- nrow(data)
num_variables <- length(data)
num_numerical <- sum(sapply(data, is.numeric))
num_non_numerical <- num_variables - num_numerical

data.frame(
  Category = c("Nombre de Observations", "Nombre de Variables", "Nombre de Variables numérique", "Nombre de variable non numérique⁄"),
  Count = c(num_observations, num_variables, num_numerical, num_non_numerical)
)
```
#
```{r}
data %>%
  head()
```
#
```{r}
fraud0 <- sum(data$isFraud == 0)

fraud1 <- sum(data$isFraud == 1)

total_count <- nrow(data)

data.frame(
  Category = c("Les transaction légitimes", "Les transactions frauduleuses","Nombre totale de transactions" ),
  Count = c(fraud0, fraud1, total_count))

```
# Plot the class of isFraud
```{r}
ggplot(data = data, aes(x = factor(isFraud), fill = factor(isFraud))) +
  geom_bar(aes(y = (..count..)/sum(..count..)),position = "dodge",alpha=0.7) + 
  geom_text(aes(y = (..count..)/sum(..count..), 
                label = paste0(..count..," ","  (",round(prop.table(..count..) * 100,2), '%',")")), 
            stat = 'count', 
            position = position_dodge(.9), 
            size=2.5,vjust = -0.3) + 
  scale_fill_manual("",values=c("#ADD8E6","#FFA07A"),labels=c("No Fraud","Fraud")) +
  labs(x = "", y = '') +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "bottom", 
        axis.text=element_blank(),
        axis.ticks = element_blank())

ggplot(data = Train_data1, aes(x = factor(isFraud), fill = factor(isFraud))) +
  geom_bar(aes(y = (..count..)/sum(..count..)),position = "dodge",alpha=0.7) + 
  geom_text(aes(y = (..count..)/sum(..count..), 
                label = paste0(..count..," ","  (",round(prop.table(..count..) * 100,2), '%',")")), 
            stat = 'count', 
            position = position_dodge(.9), 
            size=2.5,vjust = -0.3) + 
  scale_fill_manual("",values=c("#ADD8E6","#FFA07A"),labels=c("No Fraud","Fraud")) +
  labs(x = "", y = '') +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "bottom", 
        axis.text=element_blank(),
        axis.ticks = element_blank())


```
#Analyse univariate
#Variable non numérique
##Pourcentage de valeur manquante
```{r}
list_char <- names(data)[sapply(data, is.character)]
data$addr1
list_char
n_mode <- function(x, data){
  list <- data[,x]
  NROW(unique(list))
}

perc_na <- function(x, data){
  list <- data[,x]
  sum(is.na(list)/NROW(list))
}

percna <- sapply(list_char, perc_na, data)
nmode <- sapply(list_char, n_mode, data)

na_count <- data.frame(list_char, percna, nmode)

na_count %>%
  mutate(list_char = fct_reorder(list_char, percna)) %>%
  ggplot(aes(list_char, percna, fill = pourcentage)) +
  geom_col() +
  coord_flip() +
  labs(title = "le pourcentage des valeurs manquantes",
       x = "variable",
       y = "proportion")
```
#
```{r}
na_count %>%
  mutate(list_char = fct_reorder(list_char, nmode)) %>%
  ggplot(aes(list_char, nmode, fill = nmode, label = nmode)) +
  geom_col(alpha = 0.5) +
  geom_text(color = "white", position = position_stack(vjust = 0.5)) +
  scale_y_log10(limits = c(1, 100000), labels = comma)+
  coord_flip() +
  labs(title = "Number of mode",
     subtitle = "per categorical variable",
     x = "variable",
     y = "log of number")
```
#ProductCD
#Table
```{r}
table(data$ProductCD)
```
#Le graphique
```{r}
ggplot(data, aes(x = ProductCD)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Distribution of Product Codes",
       x = "Product Code",
       y = "Frequency")
```
#Card4
#summary for card4
```{r}
summary(data$card4)
```
#Le graphique
```{r}
ggplot(data, aes(x = card4)) +
  geom_bar(fill = "darkred", color = "grey") +
  labs(title = "Distribution of card4",
       x = "card4",
       y = "Frequency")
```
#Card6
#summary for card6
```{r}
summary(data$card6)
```
#le garphique
```{r}
ggplot(data, aes(x = card6)) +
  geom_bar(fill = "lightgreen", color = "grey") +
  labs(title = "Distribution of card6",
       x = "card6",
       y = "Frequency")
```
#M1-M9
```{r}
bar_plots <- list()

for (i in 1:9) {
  var_name <- paste0("M", i)
  p <- ggplot(data, aes(x = !!sym(var_name))) +
    geom_bar(fill = "skyblue", color = "black") +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Frequency")
  bar_plots[[i]] <- p
}
wrap_plots(bar_plots)
```
#P_emaildomain
#Le graphique
```{r}
ggplot(data, aes(x = P_emaildomain)) +
  geom_bar(fill="skyblue", color = "skyblue") +
  labs(title = "Distribution des adresses e-mail",
       x = "Adresse e-mail",
       y = "Fréquence") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  coord_flip()
```
#R_emaildomain
```{r}
ggplot(data, aes(x = R_emaildomain)) +
  geom_bar(fill="skyblue" ,color = "skyblue") +
  labs(title = "Distribution des adresses e-mail",
       x = "Adresse e-mail",
       y = "Fréquence") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
#DeviceType
```{r}
ggplot(data, aes(x = DeviceType)) +
  geom_bar(fill="skyblue" ,color = "skyblue") +
  labs(title = "Distribution des DeviceType",
       x = "DeviceType",
       y = "Fréquence") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
#id12 to id38
#Le graphique
```{r}
subset_data <- data[, paste0("id_", 12:20)] 
bar_plots <- list()
for (i in 1:ncol(subset_data)) {
  var_name <- colnames(subset_data)[i]
  p <- ggplot(subset_data, aes_string(x = var_name)) +
    geom_bar(fill = "skyblue", color = "black") +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Frequency") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  bar_plots[[i]] <- p
}
wrap_plots(bar_plots)
```
### Les variables numérique
##Know what are the numerical variables
```{r}
numerical_vars <- data %>% select_if(is.numeric) %>% names()
print("Numerical variables:")
print(numerical_vars)
```
##Pourcentage de NA dans les données numériques
```{r}
missing_percentage <- sapply(data, function(x) {
  if(is.numeric(x)) {
    sum(is.na(x)) / length(x) * 100
  } else {
    NA
  }
})

missing_percentage[!is.na(missing_percentage)]
```
###TransactionDT
##Creating the new Realdatatime
```{r}
reference_date <- as.POSIXct("2017-12-01 00:00:00", tz = "UTC")

timedelta <- as.difftime(data$TransactionDT, units = "secs")

real_datetime <- reference_date + timedelta

data$real_datetime <- real_datetime
```
#Date (Trying to understand the whole thing)
```{r}
library(lubridate)
train_dt <- data$real_datetime
unique(wday(train_dt))
```
#Week
```{r}
unique(week(train_dt))
```
#
```{r}
data$date <- train_dt
data$day <- wday(train_dt)
data$week <- week(train_dt)
data$hour <- hour(train_dt)
```
##summary for TransactionDT
```{r}
summary(data$day)
summary(data$week)
summary(data$hour)
```
#Graph de distribution de la variable TransactionDT
```{r}
ggplot(data, aes(x = real_datetime)) +
  geom_histogram(binwidth = 30, fill = 'blue', color = 'SKYBLUE') +
  labs(x = "Real Datetime", y = "Frequency", title = "Histogram of Real Datetime")
```
##TransactionAMT
#Summary for TransactionAMT
```{r}
summary(data$TransactionAmt)
```
#Le graphique
```{r}
ggplot(data, aes(x = TransactionAmt)) +
  geom_histogram(binwidth = 30, fill = 'blue', color = 'skyblue') +
  labs(x = "TransactionAMT", y = "Frequency", title = "Histogram of TransactionAMT")
```
##Addr1 et Addr2
#Summary for Addr1
```{r}
summary(data$addr1)
```
#Summary for Addr2
```{r}
summary(data$addr2)
```
#Le graphique de Addr1 et Addr2
```{r}
bar_plots1 <- list()
for (i in 1:2) {
  var_name1 <- paste0("addr", i)
  p1 <- ggplot(data, aes(x = !!sym(var_name1))) +
    geom_bar(fill = "darkred", color = "lightgreen") +
    labs(title = paste("Distribution of", var_name1),
         x = var_name1,
         y = "Frequency")
  bar_plots1[[i]] <- p1  
}

bar_plots1[[1]] + bar_plots1[[2]]
```
##Card1
#Summary for card1
```{r}
summary(data$card1)
```
#le graphique de card1
```{r}
ggplot(data, aes(x = card1)) +
  geom_bar(fill = "skyblue", color = "skyblue") +
  labs(title = "Distribution of card1",
       x = "card1",
       y = "Frequency")
```
##Card2
#Summary for card2
```{r}
summary(data$card2)
```
#Le graphique card2
```{r}
ggplot(data, aes(x = card2)) +
  geom_bar(fill = "skyblue", color = "darkgreen") +
  labs(title = "Distribution of card2",
       x = "card2",
       y = "Frequency")
```
##Card3
#Summary for Card3
```{r}
summary(data$card3)
```
#Le graphique card3
```{r}
ggplot(data, aes(x = card3)) +
  geom_bar(fill = "skyblue", color = "darkred") +
  labs(title = "Distribution of card3",
       x = "card3",
       y = "Frequency")
```
##Card5
#Summary for card5
```{r}
summary(data$card5)
```
#Le graphique card5
```{r}
ggplot(data, aes(x = card5)) +
  geom_bar(fill = "lightgreen", color = "grey") +
  labs(title = "Distribution of card5",
       x = "card5",
       y = "Frequency")
```
##Dist1
#summary for Dist1
```{r}
summary(data$dist1)
```
##Dist2
#summary for Dist2
```{r}
summary(data$dist2)
```
##C1-C14
```{r}
summary_C1 <- summary(data$C1)
summary_C2 <- summary(data$C2)
summary_C3 <- summary(data$C3)
summary_C4 <- summary(data$C4)
summary_C5 <- summary(data$C5)
summary_C6 <- summary(data$C6)
summary_C7 <- summary(data$C7)
summary_C8 <- summary(data$C8)
summary_C9 <- summary(data$C9)
summary_C10 <- summary(data$C10)
summary_C11 <- summary(data$C11)
summary_C12 <- summary(data$C12)
summary_C13 <- summary(data$C13)
summary_C14 <- summary(data$C14)
variable_names <- paste0("C", 1:14)
summary_table <- bind_rows(
  summary_C1,
  summary_C2,
  summary_C3,
  summary_C4,
  summary_C5,
  summary_C6,
  summary_C7,
  summary_C8,
  summary_C9,
  summary_C10,
  summary_C11,
  summary_C12,
  summary_C13,
  summary_C14,
  .id = "Variable"
)
cbind(variable = variable_names, summary_table)
```
#le graphique C1-C14
```{r}
bar_plots2 <- list()
for (i in 1:14) {
  var_name <- paste0("C", i)
  p <- ggplot(data, aes(x = !!sym(var_name))) +
    geom_bar(fill = "skyblue", color = "black") +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Frequency")
  bar_plots2[[i]] <- p
}
wrap_plots(bar_plots2)
```
##D1-D15
#Summary for D1-D15
```{r}
summary_D1 <- summary(data$D1)
summary_D2 <- summary(data$D2)
summary_D3 <- summary(data$D3)
summary_D4 <- summary(data$D4)
summary_D5 <- summary(data$D5)
summary_D6 <- summary(data$D6)
summary_D7 <- summary(data$D7)
summary_D8 <- summary(data$D8)
summary_D9 <- summary(data$D9)
summary_D10 <- summary(data$D10)
summary_D11 <- summary(data$D11)
summary_D12 <- summary(data$D12)
summary_D13 <- summary(data$D13)
summary_D14 <- summary(data$D14)
summary_D15 <- summary(data$D15)
variable_names1 <- paste0("D", 1:15)
summary_table1 <- bind_rows(
  summary_D1,
  summary_D2,
  summary_D3,
  summary_D4,
  summary_D5,
  summary_D6,
  summary_D7,
  summary_D8,
  summary_D9,
  summary_D10,
  summary_D11,
  summary_D12,
  summary_D13,
  summary_D14,
  summary_D15,
  .id = "Variable"
)
cbind(variable = variable_names1, summary_table1)
```
#Le graphique for D1-D15
```{r}
bar_plots3 <- list()
for (i in 1:15) {
  var_name <- paste0("D", i)
  p <- ggplot(data, aes(x = !!sym(var_name))) +
    geom_bar(fill = "skyblue", color = "black") +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Frequency")
  bar_plots3[[i]] <- p
}
wrap_plots(bar_plots3)
```
##id_01-id_11
#Summary for id_01-id_11
```{r}
data$id
summary_iD1 <- summary(data$id_01)
summary_iD2 <- summary(data$id_02)
summary_iD3 <- summary(data$id_03)
summary_iD4 <- summary(data$id_04)
summary_iD5 <- summary(data$id_05)
summary_iD6 <- summary(data$id_06)
summary_iD7 <- summary(data$id_07)
summary_iD8 <- summary(data$id_08)
summary_iD9 <- summary(data$id_09)
summary_iD10 <- summary(data$id_10)
summary_iD11 <- summary(data$id_11)
variable_names2 <- paste0("id_", 1:11)
summary_table2 <- bind_rows(
  summary_iD1,
  summary_iD2,
  summary_iD3,
  summary_iD4,
  summary_iD5,
  summary_iD6,
  summary_iD7,
  summary_iD8,
  summary_iD9,
  summary_iD10,
  summary_iD11,
  .id = "Variable"
)
cbind(variable = variable_names2, summary_table2)
```
#Le graphique id_01-id_11
```{r}
library(ggplot2)
bar_plots4 <- list()
for (i in 1:11) {  
  var_name <- sprintf("id_%02d", i)
  p <- ggplot(data, aes(x = !!sym(var_name))) +
    geom_bar(fill = "skyblue", color = "skyblue") +
    labs(title = paste("Distribution of", var_name),
         x = var_name,
         y = "Frequency")
  bar_plots4[[i]] <- p
}

wrap_plots(bar_plots4)
```
###Analyse bivariée
## understand and remove variables with more than 50% of missing values
```{r}
missing_rate <- colMeans(is.na(data))
missing_rate %>% sort(decreasing=T) %>% head(20) %>% print
vars_to_remove <- names(missing_rate[missing_rate > 0.50])
data1 <- data %>% select(-all_of(vars_to_remove))
```

##now we move to the understanding of the relation between the variables and the la variable cible
##Les variables quantitatives
#La relation between TransactionDT et la variable cible
```{r}
a1  <- ggplot(data1, aes(real_datetime, fill = factor(isFraud))) + geom_histogram(alpha = 0.7, bins = 30)  + theme_minimal() +
    ggtitle("TransactionDT variable") + labs(x = "TransactionDT") + theme(legend.position = "bottom")
a1
```
# Le graphique radiale de relation
```{r}
data1 %>%
  ggplot(aes((hour+1))) +
  geom_histogram(aes(y = ..density.., fill = as.factor(isFraud), color =as.factor(isFraud)), alpha = 0.4, breaks = seq(0, 24), position = "identity") + 
  scale_x_continuous("", limits = c(0, 24), breaks = seq(0, 24)) + 
  coord_polar()
```
# La realtion between TransactionAMT et la variable cible
```{r}
options(repr.plot.width = 5, repr.plot.height = 3)
a1 <- ggplot(data1, aes(TransactionAmt, fill = factor(isFraud))) + geom_histogram()
data1$amt_log  <- log10(data1$TransactionAmt)
a1 <- ggplot(data1, aes(amt_log, fill = factor(isFraud))) + geom_histogram() + ggtitle("data")
options(repr.plot.width = 10, repr.plot.height = 3)
a1
```
#La relation between card1 et la variable cible
```{r}
p1 <- options(repr.plot.width = 4, repr.plot.height = 3) +
ggplot(data1, aes(card1, fill = factor(isFraud))) + geom_histogram(alpha = 0.7, position = 'fill', bins = 50) +
geom_hline(yintercept = 0.035, colour="black", linetype="dashed") + coord_cartesian( ylim = c(0, 0.1))
```
#La relation between card2 et la variable cible
```{r}
p2 <- options(repr.plot.width = 4, repr.plot.height = 3) +
ggplot(data1, aes(card2, fill = factor(isFraud))) + geom_histogram(alpha = 0.7, position = 'fill', bins = 50) +
geom_hline(yintercept = 0.035, colour="black", linetype="dashed") + coord_cartesian( ylim = c(0, 0.2))
```
#La realtion between card3 et la variable cible
```{r}
p3 <- options(repr.plot.width = 4, repr.plot.height = 3) +
ggplot(data1, aes(card3, fill = factor(isFraud))) + geom_histogram(alpha = 0.7, position = 'fill', bins = 50) +
geom_hline(yintercept = 0.035, colour="black", linetype="dashed") + coord_cartesian( ylim = c(0, 0.2))
```
#La relation between card5 et la variable cible
```{r}
p5 <- options(repr.plot.width = 4, repr.plot.height = 3) +
ggplot(data1, aes(card5, fill = factor(isFraud))) + geom_histogram(alpha = 0.7, position = 'fill', bins = 50) +
geom_hline(yintercept = 0.035, colour="black", linetype="dashed") + coord_cartesian( ylim = c(0, 0.2))
```
## all graphs 
```{r}
data1 %>%
  select(isFraud, card1, card2, card3, card5) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "la densité des variables card1, card2, card3 et card5 vs Fraud / légitime",
       x = "valeurs",
       y = "Densité")
```



#La relation entre D1 D3 D4 D10 D15 et la variable cible
```{r}
data1 %>%
  select(isFraud, D1, D3, D4, D10, D15) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for D1, D3, D4, D10, and D15 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```

##Les variables qualitatives
#La relation between ProductCD et la variable cible
#put plot caterogical
```{r}
plot_categorical <- function(df, var){
  df %>%
    dplyr::filter(column == var) %>%
    dplyr::group_by(value, isFraud) %>%
    dplyr::summarize(tot = n()) %>%
    ggplot2::ggplot(aes(x = value, y = tot, fill = value)) +
    ggplot2::geom_col(alpha = 0.3, position = "identity") +
    ggplot2::facet_wrap(~isFraud, scales = "free") +
    ggplot2::labs(title = paste0(var, " vs Fraud / Legit"),
                  x = "Value",
                  y = "Number of Transactions") +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
}
```
#Le graphique
```{r}
Pcd_ana <- data1 %>%
  select(isFraud, ProductCD) %>%
  gather(column, value, -isFraud)

print(plot_categorical(Pcd_ana, "ProductCD"))
```
#La relation between card4 & card6 et la variable cible
```{r}
card_ana <- data1 %>%
  select(isFraud, card1:card6) %>%
  tidyr::gather(column, value, -isFraud)

for(var in c("card4", "card6")){
  print(plot_categorical(card_ana, var))
}
```
#La relation entre Addr1 et la variable cible
```{r}
data1 %>%
  select(isFraud, addr1) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free")+
  labs(title = "Density for addr1 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```
#La relation entre addr2 et la variable cible
```{r}
data1 %>%
  select(isFraud, addr2) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free")+
  labs(title = "Density for addr2 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```
#La relation entre la variable M4 et la variable cible
```{r}
M_ana <- data1 %>%
  select(isFraud, M4) %>%
  tidyr::gather(column, value, -isFraud)

for(var in c("M4")){
  print(plot_categorical(M_ana, var))
}
```
#La relation entre la variable M6 et la variable cible
```{r}
M_ana <- data1 %>%
  select(isFraud, M6) %>%
  tidyr::gather(column, value, -isFraud)

for(var in c("M6")){
  print(plot_categorical(M_ana, var))
}
```
#La relation between P-emaildomain et la variable cible
```{r}
PDomain_ana <- data1 %>%
  select(isFraud,P_emaildomain ) %>%
  gather(column, value, -isFraud)

my_colors <- c("#FF9999", "#66CC99")

ggplot(PDomain_ana, aes(x = value, fill = factor(isFraud))) +
  geom_bar(position = "dodge") +
  labs(title = "Count Plot for domain features",
       x = "Domain Features",
       y = "Count") +
  scale_fill_manual(values = my_colors) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
#La reltion entre C1-C14 avec la variable cible
```{r}
data1 %>%
  select(isFraud, C1:C14) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for C1 to C14 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```

#La relation entre les Vxx (V12-V50) et la variable cible
```{r}
data1 %>%
  select(isFraud, V12:V50) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for V12 to V50 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```
#V51-V89
```{r}
data1 %>%
  select(isFraud, V51:V89) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for V51 to V89 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```

#V90-V128
```{r}
data1 %>%
  select(isFraud, V90:V128) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for V90 to V128 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```
#V129-V137
```{r}
data1 %>%
  select(isFraud, V129:V137) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for V128 to V137 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```
#V279-V321
```{r}
data1 %>%
  select(isFraud, V279:V321) %>%
  gather(column, value, -isFraud) %>%
  filter(value > 0) %>%  
  ggplot() +
  geom_density(aes(value, color = as.factor(isFraud), fill = as.factor(isFraud)), alpha = 0.5) +
  scale_x_log10() +
  facet_wrap(~column, scales = "free") +
  labs(title = "Density for V279 to V321 vs Fraud / Legit",
       subtitle = "Value <= 0 removed for log scale",
       x = "values",
       y = "Density")
```
## Now dealing with missing values
#let's remmember how much we have still of na for the varibles
```{r}
missing_rate1 <- colMeans(is.na(data1))
missing_rate1 %>% sort(decreasing=T) %>% head(100) %>% print
```
####Data processing 
#Préparation de la base train
#un tableau qui regroupe toute les informations concernant la base train 
```{r}
write.csv(data1, "output_file.csv", row.names = FALSE)
```
#Data processing 
#Préparation de la base train
```{r}
set.seed(2001)
data_split <- initial_split(data1, prop = 0.75, strata = isFraud)
train_data <- training(data_split)
test_data <- testing(data_split)
```
#un tableau qui regroupe toute les informations concernant la base train 
```{r}
num_obs <- dim(train_data)[1]
num_vars_total <- dim(train_data)[2]
num_vars_numeric <- sum(sapply(train_data, is.numeric))
num_vars_non_numeric <- num_vars_total - num_vars_numeric
data.frame(
  "Nombre d'observations" = num_obs,
  "Nombre de variables" = num_vars_total,
  "Nombre de variables numériques" = num_vars_numeric,
  "Nombre de variables non numériques" = num_vars_non_numeric
)
```
#un tableau qui regroupe toute les informations concernant la base train
```{r}
num_obs <- dim(test_data)[1]
num_vars_total <- dim(test_data)[2]
num_vars_numeric <- sum(sapply(test_data, is.numeric))
num_vars_non_numeric <- num_vars_total - num_vars_numeric
data.frame(
  "Nombre d'observations" = num_obs,
  "Nombre de variables" = num_vars_total,
  "Nombre de variables numériques" = num_vars_numeric,
  "Nombre de variables non numériques" = num_vars_non_numeric
)
```





