---
title: "H2O machine Dev"
author: "MEZIANE AHMED YACINE"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Les packages
```{r}
library(tidyverse)
library(tidymodels)
library(tidyselect)
library(MLmetrics)
library(lightgbm)
library(data.table)
library(moments)
library(moments)
library(MLmetrics)
library(ggthemes)
library(ggmosaic)
library(gridExtra)
library(repr)
library(data.table)
library(fastDummies)
library(tictoc)
library(naniar)
library(DataExplorer)
library(lubridate)
library(patchwork)
library(corrplot)
library(kableExtra)
library(themis)
library(doParallel)
library(DMwR2)
library(h2o)
```
###Initialize H2O
```{r}
h2o.init()
```
## upload data
```{r}
train_iden <- read_csv("/Users/macmo/Desktop/Mémoire/Base de donnée/ieee-fraud-detection/train_identity.csv")
train_trans <- read_csv("/Users/macmo/Desktop/Mémoire/Base de donnée/ieee-fraud-detection/train_transaction.csv")
```
#creating full data
```{r}
data<- train_trans  %>% 
  left_join(train_iden,by="TransactionID")
rm(train_iden,train_trans)
```
## features engeniring 
```{r}
data <- data %>%
  mutate(TransactionAmt_Log = log1p(TransactionAmt),
         TransactionAmt_to_mean_card1 = TransactionAmt / ave(TransactionAmt, card1, FUN = mean),
         TransactionAmt_to_mean_card4 = TransactionAmt / ave(TransactionAmt, card4, FUN = mean))
```

#TransactionDT
```{r}
reference_date <- as.POSIXct("2017-12-01 00:00:00", tz = "UTC")

timedelta <- as.difftime(data$TransactionDT, units = "secs")

real_datetime <- reference_date + timedelta

data$real_datetime <- real_datetime
```
#Date (Trying to understand the whole thing)
```{r}
library(lubridate)
train_dt <- data$real_datetime
unique(wday(train_dt))
```

#
```{r}
data$date <- train_dt
data$day <- wday(train_dt)
```
## understand and remove variables with more than 50% of missing values
```{r}
missing_rate <- colMeans(is.na(data))
missing_rate %>% sort(decreasing=T) %>% head(20) %>% print
vars_to_remove <- names(missing_rate[missing_rate > 0.50])
data1 <- data %>% select(-all_of(vars_to_remove))
```
## Split the data into training and validation sets
```{r}
set.seed(2001)
data_split <- initial_split(data1, prop = 0.75, strata = isFraud)
train_data <- training(data_split)
test_data <- testing(data_split)
```
## Exclude TransactionID and TransactionDT from the training data
```{r}
train_data <- train_data %>%
  select(-TransactionID, -TransactionDT, -real_datetime, -date)
```
## recipe
```{r}
recipe_obj <- recipe(isFraud ~ ., data = train_data) %>%
  step_mutate(M6 = as.factor(M6)) %>%
  step_impute_mode(M6) %>%
  step_impute_mean(all_numeric_predictors()) %>% 
  step_impute_mode(all_nominal_predictors()) %>%
  step_nzv(all_numeric_predictors()) %>% 
  step_corr(all_numeric_predictors(), threshold = 0.9) %>%
  step_normalize(all_numeric_predictors()) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_mutate(isFraud = as.factor(isFraud)) %>% 
  step_upsample(over_ratio = 1)
```

## prep
```{r}
recipe_fit <- prep(recipe_obj, training = train_data)
```
## bake the new data
```{r}
Train_data1 <- bake(recipe_fit, new_data = train_data)
test_data1 <- bake(recipe_fit, new_data = test_data)
```
#Define the target and features
```{r}
target <- "isFraud"
features <- setdiff(names(Train_data1), target)
```
## Convert to H2O frames
```{r}
train_h2o <- as.h2o(Train_data1)
valid_h2o <- as.h2o(test_data1)
```
# impute numerical data
```{r}
for (col in numeric_cols) {
  h2o.impute(train_h2o, col, method = "mean")
}
```

### Define the model
```{r}
rf_model <- h2o.randomForest(
  x = features1,
  y = target1,
  training_frame = train_h2o1,
  validation_frame = valid_h2o1,
  ntrees = 1500,
  max_depth = 10,
  min_rows = 600,
  stopping_rounds = 5,
  score_tree_interval = 10,
  balance_classes = TRUE,
  stopping_metric = "AUC",
  stopping_tolerance = 0.001,
  max_runtime_secs = 500
)
```
## prediction
```{r}
predictions <- h2o.predict(rf_model, valid_h2o)
predictions
```

## confusion matrix
```{r}
h2o.confusionMatrix(rf_model, valid_h2o1)
```


## performance model 
```{r}
h2o.confusionMatrix(rf_model, train_h2o1)
```
# PR AUC
```{r}
perf1 <- h2o.performance(rf_model, valid_h2o1)
h2o.auc(perf1)
h2o.aucpr(perf1)
perf <- h2o.performance(rf_model, train_h2o1)
h2o.aucpr(perf)
h2o.auc(perf)
```
## AUC ROC
```{r}
h2o.aucpr(perf)
h2o.auc(perf1)
```
##
```{r}
h2o.accuracy(perf,threshold =0.391764397834652)
h2o.precision(perf, threshold = 0.391764397834652)
h2o.recall(perf, threshold = 0.391764397834652)
h2o.specificity(perf,threshold = 0.391764397834652)
h2o.mean_per_class_accuracy(perf,threshold = 0.391764397834652)
h2o.mean_per_class_error(perf)
```


## gainlift
```{r}
h2o.gains_lift(rf_model, valid_h2o)
```
## plot
```{r}
metrics <- as.data.frame(h2o.metric(perf))
metrics1 <- as.data.frame(h2o.metric(perf1))
valid_df <- as.data.frame(valid_h2o1)
valid_df1 <- as.data.frame(train_h2o1)
positive_class_proportion <- sum(valid_df$isFraud == 1) / nrow(valid_df1)
metrics %>% ggplot(aes(x = recall, y = precision)) +
  geom_line(color = "darkred", size = 1) +
  geom_hline(yintercept = positive_class_proportion + 0.05, linetype = "dashed", color = "blue", size = 1) +
  annotate("text", x = 0.5, y = positive_class_proportion, label = "No Skill", color = "blue") +
  labs(title = "Precision-Recall Curve",
       x = "Recall",
       y = "Precision") +
  theme(plot.title = element_text(hjust = 0.5)) +
    theme_minimal()
```
##
# Plot AUC ROC
```{r}
plot(perf)
```

# Convert to data frame for ggplot2
```{r}
pr_curve_df <- as.data.frame(pr_curve)
```
# Plot the most important variables
```{r}
h2o.varimp(rf_model)
h2o.varimp_plot(rf_model)
```
## pr_auc matrix
```{r}
h2o.auc(perf1)
h2o.aucpr(perf1)
h2o.aucpr(rf_model)
```
## VALID H2O
# Statistique
```{r}
h2o.accuracy(perf1,threshold =0.410004894012808)
h2o.precision(perf1,threshold =0.410004894012808)
h2o.recall(perf1,threshold =0.410004894012808)
h2o.specificity(perf1,threshold =0.410004894012808)
h2o.mean_per_class_accuracy(perf1,threshold =0.410004894012808)
h2o.mean_per_class_error(perf1)
```
##PR_AUC
```{r}
positive_class_proportion <- sum(valid_df$isFraud == 1) / nrow(valid_df1)
metrics1 %>% ggplot(aes(x = recall, y = precision)) +
  geom_line(color = "darkred", size = 1) +
  geom_hline(yintercept = positive_class_proportion, linetype = "dashed", color = "blue", size = 1) +
  annotate("text", x = 0.5, y = positive_class_proportion + 0.02, label = "No Skill", color = "blue") +
  labs(title = "Precision-Recall Curve",
       x = "Recall",
       y = "Precision") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()
```

```{r}
pr_auc <- h2o.auc(pr_auc = TRUE, perf2)
print(paste("PR AUC:", pr_auc))
```
## plot auc train
```{r}
plot(perf1)
```
## test
```{r}
plot(perf2)
h2o.aucpr(perf2)
h2o.auc(perf2)
```
## importance variable
```{r}
immp<- h2o.varimp(rf_model)
head(immp, 20)
```

