---
title: "NBh2o"
author: "MEZIANE AHMED YACINE"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Les packages
```{r}
library(tidyverse)
library(tidymodels)
library(tidyselect)
library(MLmetrics)
library(lightgbm)
library(data.table)
library(moments)
library(moments)
library(MLmetrics)
library(ggthemes)
library(ggmosaic)
library(gridExtra)
library(repr)
library(data.table)
library(fastDummies)
library(tictoc)
library(naniar)
library(DataExplorer)
library(lubridate)
library(patchwork)
library(corrplot)
library(kableExtra)
library(themis)
library(doParallel)
library(DMwR2)
library(h2o)
library(agua)
```
###Initialize H2O
```{r}
h2o.init()
```
## upload data
```{r}
train_iden1 <- read_csv("/Users/macmo/Desktop/Mémoire/Base de donnée/ieee-fraud-detection/train_identity.csv")
train_trans1 <- read_csv("/Users/macmo/Desktop/Mémoire/Base de donnée/ieee-fraud-detection/train_transaction.csv")
```
#creating full data
```{r}
data1<- train_trans1  %>% 
  left_join(train_iden1,by="TransactionID")
rm(train_iden1,train_trans1)
```
## Feautures engenirieng
# Interaction Features
```{r}
data1 <- data1 %>%
  mutate(TransactionAmt_Log = log1p(TransactionAmt),
         TransactionAmt_to_mean_card1 = TransactionAmt / ave(TransactionAmt, card1, FUN = mean),
         TransactionAmt_to_mean_card4 = TransactionAmt / ave(TransactionAmt, card4, FUN = mean))

```

#TransactionDT
```{r}
reference_date1 <- as.POSIXct("2017-12-01 00:00:00", tz = "UTC")

timedelta1 <- as.difftime(data1$TransactionDT, units = "secs")

real_datetime1 <- reference_date1 + timedelta1

data1$real_datetime1 <- real_datetime1
```
#Date (Trying to understand the whole thing)
```{r}
library(lubridate)
train_dt1 <- data1$real_datetime1
unique(wday(train_dt1))
```
#
```{r}
data1$date <- train_dt1
data1$day <- wday(train_dt1)
```

## understand and remove variables with more than 50% of missing values
```{r}
missing_rate1 <- colMeans(is.na(data1))
missing_rate1 %>% sort(decreasing=T) %>% head(20) %>% print
vars_to_remove1 <- names(missing_rate1[missing_rate1 > 0.50])
data2 <- data1 %>% select(-all_of(vars_to_remove1))
```
## Split the data into training and validation sets
```{r}
set.seed(2001)

data2 <- data2 %>% 
  mutate(isFraud =as.factor(isFraud))

data_split1 <- initial_split(data2, prop = 0.75, strata = isFraud)
train_data1 <- training(data_split1)
test_data1 <- testing(data_split1)
```
## recipe
```{r}
recipe_obj1 <- recipe(isFraud ~ ., data = train_data1) %>%
  step_mutate(M6 = as.factor(M6)) %>%
  step_select(-TransactionID, -TransactionDT, -real_datetime1, -date) %>%
  step_impute_mode(M6) %>%
  step_impute_mean(all_numeric_predictors()) %>%
  step_impute_mode(all_nominal_predictors()) %>%
  step_nzv(all_numeric_predictors()) %>%
  step_corr(all_numeric_predictors(), threshold = 0.9) %>%
  step_normalize(all_numeric_predictors()) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_smote(isFraud,neighbors = 10,over_ratio = 0.5)

recipe_obj1
```
```{r}
Train_data2 <- recipe_obj1 %>% prep(training = train_data1) %>% juice()
Test_data2 <- recipe_obj1 %>% prep(training = test_data1) %>% juice()
```

## prep
```{r}
# recipe_fit1 <- prep(recipe_obj1, training = train_data1)
# 
# recipe_fit1
```
## bake the new data
```{r}
# Train_data2 <- bake(recipe_fit1, new_data = train_data1)
# test_data2 <- bake(recipe_fit1, new_data = test_data1)
```
#Define the target and features
```{r}
target1 <- "isFraud"
features1 <- setdiff(names(Train_data2), target1)
```
## Convert to H2O frames
```{r}
train_h2o1 <- as.h2o(Train_data2)
valid_h2o1 <- as.h2o(Test_data2)
```
### Define the model
```{r}
xg_model <- h2o.xgboost(
  x = features1,
  y = target1,
  training_frame = train_h2o1,
  validation_frame = valid_h2o1,
  seed = 2001,
  stopping_metric = "AUC",
  stopping_rounds = 5,
  stopping_tolerance = 0.001,
  sample_rate = 1,
  learn_rate = 0.4,
  max_runtime_secs = 600,
   ntrees = 2700,
  max_depth = 10,
  min_rows = 600,
  score_each_iteration = TRUE
)
```
## Calculate performance metrics
```{r}
perf4 <- h2o.performance(xg_model, newdata = valid_h2o1)
perf3 <- h2o.performance(xg_model, newdata = train_h2o1)
h2o.auc(xg_model)
h2o.aucpr(xg_model)
h2o.aucpr(perf3)
h2o.aucpr(perf4)
h2o.auc(perf3)
h2o.auc(perf4)
```
## confusion matrix pour train
```{r}
h2o.confusionMatrix(xg_model, train_h2o1)
```



## confusion matrix pour test
```{r}
h2o.confusionMatrix(xg_model, valid_h2o1)
h2o.confusionMatrix()
```
# Plot the most important variables
```{r}
h2o.varimp(xg_model)
h2o.varimp_plot(xg_model)
```
## 
```{r}
h2o.accuracy(perf3, threshold = 0.423992688531306)
h2o.precision(perf3, threshold = 0.423992688531306)
h2o.recall(perf3, threshold = 0.423992688531306)
h2o.specificity(perf3, threshold = 0.423992688531306)
h2o.mean_per_class_accuracy(perf3, threshold = 0.423992688531306)
h2o.mean_per_class_error(perf3)
```
## plot TRAIN
```{r}
metrics3 <- as.data.frame(h2o.metric(perf3))
metrics4 <- as.data.frame(h2o.metric(perf4))
valid_df3 <- as.data.frame(valid_h2o1)
valid_df4 <- as.data.frame(train_h2o1)

positive_class_proportion <- sum(valid_df3$isFraud == 1) / nrow(valid_df4)
metrics3 %>% ggplot(aes(x = recall, y = precision)) +
  geom_line(color = "darkred", size = 1) +
  geom_hline(yintercept = positive_class_proportion +0.035, linetype = "dashed", color = "blue", size = 1) +
  annotate("text", x = 0.5, y = positive_class_proportion, label = "No Skill", color = "blue") +
  labs(title = "Precision-Recall Curve",
       x = "Recall",
       y = "Precision") +
  theme(plot.title = element_text(hjust = 0.5)) +
    theme_minimal()
```


## PLOT TEST
```{r}
positive_class_proportion <- sum(valid_df4$isFraud == 1) / nrow(valid_df4)
metrics4 %>% ggplot(aes(x = recall, y = precision)) +
  geom_line(color = "darkred", size = 1) +
  geom_hline(yintercept = positive_class_proportion, linetype = "dashed", color = "blue", size = 1) +
  annotate("text", x = 0.5, y = positive_class_proportion, label = "No Skill", color = "blue") +
  labs(title = "Precision-Recall Curve",
       x = "Recall",
       y = "Precision") +
  theme(plot.title = element_text(hjust = 0.5)) +
    theme_minimal()
```
## statistique 
```{r}
h2o.accuracy(perf4, thresholds =0.997679613090045)
h2o.precision(perf4, threshold = 0.997679613090045)
h2o.recall(perf4, threshold = 0.997679613090045)
h2o.specificity(perf4,threshold = 0.997679613090045)
h2o.mean_per_class_accuracy(perf4,threshold = 0.999997324553075)
h2o.mean_per_class_error(perf4)
```
## statistique test
```{r}
h2o.accuracy(perf3, thresholds = 0.423581700772047)
h2o.precision(perf3, threshold = 0.423581700772047)
h2o.recall(perf3, threshold = 0.423581700772047)
h2o.specificity(perf3,threshold = 0.423581700772047)
h2o.mean_per_class_accuracy(perf3,threshold = 0.423581700772047)
h2o.mean_per_class_error(perf3)
```
## auc_ pr & auc
```{r}
h2o.auc(xg_model)
h2o.aucpr(xg_model)
```
## plot train
```{r}
plot(perf4)
```

## test
```{r}
plot(perf3)
```
## variable importance 
```{r}
imp <- h2o.varimp(xg_model)
head(imp, 20)
```
## plot
```{r}
h2o.varimp_plot(xg_model)
```
##
```{r}
pred_train <- h2o.predict(xg_model, train_h2o1)
pred_test <- h2o.predict(xg_model, valid_h2o1)
```

## graph after unballanced 
```{r}
ggplot(data = Train_data2, aes(x = factor(isFraud), fill = factor(isFraud))) +
  geom_bar(aes(y = (..count..)/sum(..count..)),position = "dodge",alpha=0.7) + 
  geom_text(aes(y = (..count..)/sum(..count..), 
                label = paste0(..count..," ","  (",round(prop.table(..count..) * 100,2), '%',")")), 
            stat = 'count', 
            position = position_dodge(.9), 
            size=2.5,vjust = -0.3) + 
  scale_fill_manual("",values=c("#ADD8E6","#FFA07A"),labels=c("No Fraud","Fraud")) +
  labs(x = "", y = '') +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "bottom", 
        axis.text=element_blank(),
        axis.ticks = element_blank())
```

